---
title: "Home Credit Dafault Risk: EDA"
author: "kotsubo takuto"
output: 
    html_document:
      md_extensions: -ascii_identifiers
      toc: true
      toc_depth: 3
      code_folding: hide
---
    
# About the competition

## Overview

- 多くの人々は, クレジット履歴の不足や欠如により, ローン契約に奮闘している.
そして不幸なことにこのような人々はしばしば, 信頼できない貸し手を利用している.

- そこでクレジット履歴に代替する, 電気通信会社や取引情報などを用いて, 対象者の返済能力を予測する.

## Data description

- application_{train|test}.csv (122|121 variables)
    - Key variable: SK_ID_CURR
    - Objective variable: TARGET(1:返済困難, 0: other, 連続値)
    - About: 全てのアプリケーションのデータ
- bureau.csv (17 variables)
    - Key variable: SK_ID_CURR, SK_ID_BUREAU 
    - About: 以前使用していた, 融資の履歴
- bureau_balance.csv (3 variables)
    - Key variable: SK_ID_BUREAU
    - About: `bureau.csv`の補助データ
    - MONTHS_BALANCE: 利用日に対応した, 月次のバランス?
    - STATUS: 月次のステータス, (active, closed, DPD0-30,… [C means closed, X means status unknown, 0 means no DPD, 1 means maximal did during month between 1-30, 2 means DPD 31-60,… 5 means DPD 120+ or sold or written off ] )
- previous_applications.csv (37 variables)
    - Key variable: SK_ID_CURR, SK_ID_PREV
    - About: サンプルで融資を受けているお客様のホームクレジットローンのすべての以前のアプリケーション
- installments_payment.csv (8 variables)
    - Key variable: SK_ID_CURR, SK_ID_PREV
    - About: ローンの各月の支払い履歴
- POS_CASH_balance.csv (8 variables)
    - Key variable: SK_ID_CURR, SK_ID_PREV
    - About: 各月毎のクレジット履歴,月次バランス
- credit_card_balance.csv (23 variavbles)
    - Key variable: SK_ID_CURR, SK_ID_PREV
    - About: 各月毎のクレジットカード履歴,月次バランス
    
## Kernel sample

- [xgboost](http://rtokei.tech/machine-learning/機械学習アルゴリズム〜xgboost〜/)
- [xgboust use all columns](https://www.kaggle.com/kailex/tidy-xgb-all-tables-0-796)
- [missing value pattern](https://www.kaggle.com/jpmiller/patterns-of-missing-data)

# Setting{.tabset .tabset-fade .tabset-pills}

## knitr option

```{r reset, include=FALSE}
# 初期化
rm(list = ls())
```

```{r set up, message=FALSE}
# set directory
setwd("~/Desktop/Home_Credit_Kaggle/") 
# max.print 
options(max.print="200", digits=5)
# Global options
library(knitr)
opts_chunk$set(echo=TRUE,
               # cache = FALSE,
	             prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

## Library package

```{r package, message=FALSE}
library(tidyverse)
library(readr) # for csv
library(summarytools) # summary easily for EDA
library(GGally) # ggpairs
library(skimr) 
library(janitor)
```

## Load funciton

```{r}
source('~/Desktop/Home_Credit_Kaggle/script/function.R') # for preprocessing
source('~/Desktop/Home_Credit_Kaggle/script/makedummies.R') # for preprocessing
```

## Import csv

- Import raw data from `csv/~.csv`
- Define missing values: na = c("XNA","NA","","NaN","?",...)
- Convert charcter's columns into factor's columns 
- Delete duplicate column names and change them to lower case
- Add keyword to columns names for each data except for key columns: (_app,_bureau,_pre,_pos,_ins,_cre) 

```{r cache=TRUE}
# 訓練データ, テストデータ
app_train <- read_csv("~/Desktop/Home_Credit_Kaggle/input/csv/application_train.csv",na = c("XNA","NA","","NaN","?")) %>% 
  mutate_if(is.character, funs(factor(.))) %>% 
  clean_names() %>% # change small letters
  rename_if(!str_detect(names(.),"sk_id"),. %>% tolower %>% str_c("_app",sep=""))
app_test <- read_csv("~/Desktop/Home_Credit_Kaggle/input/csv/application_test.csv",na = c("XNA","NA","","NaN","?")) %>% 
  mutate_if(is.character, funs(factor(.))) %>% 
  clean_names() %>% # change small letters
  rename_if(!str_detect(names(.),"sk_id"),. %>% tolower %>% str_c("_app",sep=""))
# クレジット利用履歴 (by Credit Bureau)
bureau <- read_csv("~/Desktop/Home_Credit_Kaggle/input/csv/bureau.csv",na = c("XNA","NA","","NaN","?")) %>% 
  mutate_if(is.character, funs(factor(.))) %>% 
  clean_names() %>% # change small letters
  rename_if(!str_detect(names(.),"sk_id"),. %>% tolower %>% str_c("_bur",sep=""))
bureau_balance <- read_csv("~/Desktop/Home_Credit_Kaggle/input/csv/bureau_balance.csv",na = c("XNA","NA","","NaN","?")) %>% 
  mutate_if(is.character, funs(factor(.))) %>% 
  clean_names() %>% # change small letters
  rename_if(!str_detect(names(.),"sk_id"),. %>% tolower %>% str_c("_bur",sep=""))

# 過去の利用データ
previous_app <- read_csv("~/Desktop/Home_Credit_Kaggle/input/csv/previous_application.csv",na = c("XNA","NA","","NaN","?")) %>% 
  mutate_if(is.character, funs(factor(.))) %>% 
  clean_names() %>% # change small letters
  rename_if(!str_detect(names(.),"sk_id"),. %>% tolower %>% str_c("_pre",sep=""))
install_pay <- read_csv("~/Desktop/Home_Credit_Kaggle/input/csv/installments_payments.csv",na = c("XNA","NA","","NaN","?")) %>% 
  mutate_if(is.character, funs(factor(.))) %>% 
  clean_names() %>% # change small letters
  rename_if(!str_detect(names(.),"sk_id"),. %>% tolower %>% str_c("_ins",sep=""))

pos_cash <- read_csv("~/Desktop/Home_Credit_Kaggle/input/csv/POS_CASH_balance.csv",na = c("XNA","NA","","NaN","?")) %>% 
  mutate_if(is.character, funs(factor(.))) %>% 
  clean_names() %>% # change small letters
  rename_if(!str_detect(names(.),"sk_id"),. %>% tolower %>% str_c("_pos",sep=""))
credit_card <- read_csv("~/Desktop/Home_Credit_Kaggle/input/csv/credit_card_balance.csv",na = c("XNA","NA","","NaN","?")) %>% 
  mutate_if(is.character, funs(factor(.))) %>% 
  clean_names() %>% # change small letters
  rename_if(!str_detect(names(.),"sk_id"),. %>% tolower %>% str_c("_cre",sep=""))

# submit style file
# sample_submission <- read_csv("~/Desktop/Home_Credit_Kaggle/input/csv/sample_submission.csv")
```

## Export csv

- Export modified data to `csv_imp0/~.csv`
- not execute

```{r eval=FALSE}
write_csv(app_train, "~/Desktop/Home_Credit_Kaggle/input/csv_imp0/application_train.csv")
write_csv(app_test, "~/Desktop/Home_Credit_Kaggle/input/csv_imp0/application_test.csv")
write_csv(bureau, "~/Desktop/Home_Credit_Kaggle/input/csv_imp0/bureau.csv")
write_csv(bureau_balance, "~/Desktop/Home_Credit_Kaggle/input/csv_imp0/bureau_balance.csv")
write_csv(credit_card, "~/Desktop/Home_Credit_Kaggle/input/csv_imp0/credit_card_balance.csv")
write_csv(install_pay, "~/Desktop/Home_Credit_Kaggle/input/csv_imp0/installments_payments.csv")
write_csv(pos_cash, "~/Desktop/Home_Credit_Kaggle/input/csv_imp0/POS_CASH_balance.csv")
write_csv(previous_app, "~/Desktop/Home_Credit_Kaggle/input/csv_imp0/previous_application.csv")
```

## Extract col names

- not execute

```{r eval=FALSE}
tmp <- (app_train %>% head(0)) %>% 
  cbind(bureau %>% head(0)) %>% 
  cbind(bureau_balance %>% head(0)) %>% 
  cbind(pos_cash %>% head(0)) %>% 
  cbind(credit_card %>% head(0)) %>% 
  cbind(previous_app %>% head(0)) %>%
  cbind(install_pay %>% head(0)) %>% 
  colnames() %>% data.frame(new = .) 
write_csv(tmp,"~/Desktop/Home_Credit_Kaggle/data/new_column_names.csv")
# tmp %>% filter(str_detect(new,"id"))
```

# Explatory Data Analysis

- Check the data to confirm outliers and missing data 
- Confirm relationship with target variables
- Apply glimpse, skimr and dfsummary to the all data
- Check the data to confirm the uniqueness 
- Confirm that "_add" and "_imp" are not included in the data
- Make a simple combine data 

## Check missing values and outiers valules {.tabset .tabset-fade .tabset-pills}

### app_train

```{r cache=TRUE}
CheckMissingValue(app_train)
```

### app_test

```{r cache=TRUE}
CheckMissingValue(app_test)
```

### bureau

```{r cache=TRUE}
CheckMissingValue(bureau)
```

### bureau_balance

```{r cache=TRUE}
CheckMissingValue(bureau_balance)
```

### previous_app

```{r cache=TRUE}
CheckMissingValue(previous_app)
```

### install_pay

```{r cache=TRUE}
CheckMissingValue(install_pay)
```

### pos_cash

```{r cache=TRUE}
CheckMissingValue(pos_cash)
```

### credit_card

```{r cache=TRUE}
CheckMissingValue(credit_card)
```

## Relationship with target values

```{r}
app_train %>% 
  tabyl(name_contract_type_app,target_app) %>% 
  adorn_percentages("row")
app_train %>% 
  tabyl(code_gender_app,target_app) %>% 
  adorn_percentages("row")
app_train %>% 
  tabyl(flag_own_car_app,target_app) %>% 
  adorn_percentages("row")
app_train %>% 
  tabyl(flag_own_realty_app,target_app) %>% 
  adorn_percentages("row")
app_train %>% 
  tabyl(name_type_suite_app,target_app) %>% 
  adorn_percentages("row")
app_train %>% 
  tabyl(name_income_type_app,target_app) %>% 
  adorn_percentages("row")
app_train %>% 
  tabyl(name_education_type_app,target_app) %>% 
  adorn_percentages("row")
app_train %>% 
  tabyl(name_family_status_app,target_app) %>% 
  adorn_percentages("row")
app_train %>% 
  tabyl(name_housing_type_app,target_app) %>% 
  adorn_percentages("row")
app_train %>% 
  tabyl(occupation_type_app,target_app) %>% 
  adorn_percentages("row")
app_train %>% 
  tabyl(weekday_appr_process_start_app,target_app) %>% 
  adorn_percentages("row")
app_train %>% 
  tabyl(organization_type_app,target_app) %>% 
  adorn_percentages("row")
app_train %>% 
  tabyl(fondkapremont_mode_app,target_app) %>% 
  adorn_percentages("row")
app_train %>% 
  tabyl(housetype_mode_app,target_app) %>% 
  adorn_percentages("row")
app_train %>% 
  tabyl(wallsmaterial_mode_app,target_app) %>% 
  adorn_percentages("row")
app_train %>% 
  tabyl(emergencystate_mode_app,target_app) %>% 
  adorn_percentages("row")
```

## glimpse package{.tabset .tabset-fade .tabset-pills}

- check column type each data frame

### app_train

```{r cache=TRUE}
glimpse(app_train)
```

### app_test

```{r cache=TRUE}
glimpse(app_test)
```

### bureau

```{r cache=TRUE}
glimpse(bureau)
```

### bureau_balance

```{r cache=TRUE}
glimpse(bureau_balance)
```

### previous_app

```{r cache=TRUE}
glimpse(previous_app)
```

### install_pay

```{r cache=TRUE}
glimpse(install_pay)
```

### pos_cash

```{r cache=TRUE}
glimpse(pos_cash)
```

### credit_card

```{r cache=TRUE}
glimpse(credit_card)
```

## skim package{.tabset .tabset-fade .tabset-pills}

- overview of a data frame

### app_train

```{r cache=TRUE}
skimr::skim_to_wide(app_train) %>% kable()
```

### app_test

```{r cache=TRUE}
skimr::skim_to_wide(app_test) %>% kable()
```

### bureau

```{r cache=TRUE}
skimr::skim_to_wide(bureau) %>% kable()
```

### bureau_balance

```{r cache=TRUE}
skimr::skim_to_wide(bureau_balance) %>% kable()
```

### previous_app

```{r cache=TRUE}
skimr::skim_to_wide(previous_app) %>% kable()
```

### install_pay

```{r cache=TRUE}
skimr::skim_to_wide(install_pay) %>% kable()
```

### pos_cash

```{r cache=TRUE}
skimr::skim_to_wide(pos_cash) %>% kable()
```

### credit_card

```{r cache=TRUE}
skimr::skim_to_wide(credit_card) %>% kable()
```

## summarytools package{.tabset .tabset-fade .tabset-pills}

- Summary of data frame (split factor value and numeric value)

### app_train

```{r cache=TRUE}
dfSummarySplit(app_train)
```

### app_test

```{r cache=TRUE}
dfSummarySplit(app_test)
```

### bureau

```{r cache=TRUE}
dfSummarySplit(bureau)
```

### bureau_balance

```{r cache=TRUE}
dfSummarySplit(bureau_balance)
```

### previous_app

```{r cache=TRUE}
dfSummarySplit(previous_app)
```

### install_pay

```{r cache=TRUE}
dfSummarySplit(install_pay)
```

### pos_cash

```{r cache=TRUE}
dfSummarySplit(pos_cash)
```

### credit_card

```{r cache=TRUE}
dfSummarySplit(credit_card)
```

## Confirm that "_add" and "_imp" are not included in the data

```{r}
patterns <- c("_add","_imp")
CheckColumnsNotInclude(app_train,patterns)
CheckColumnsNotInclude(app_test,patterns)
CheckColumnsNotInclude(bureau,patterns)
CheckColumnsNotInclude(bureau_balance,patterns)
CheckColumnsNotInclude(credit_card,patterns)
CheckColumnsNotInclude(install_pay,patterns)
CheckColumnsNotInclude(pos_cash,patterns)
CheckColumnsNotInclude(previous_app,patterns)
```

## Make a simple combine data{.tabset .tabset-fade .tabset-pills}

- Make a all_{train|test}.csv
- Export modified data to `csv_imp0/all_{train|test}.csv`
- Apply skimr and dfsummary to the all data

### Make a combine data

```{r cache=TRUE}
bureau_sum <- makedummies(bureau_balance,basal_level = TRUE) %>% # make dummy
  SummarizeFunc(group = "sk_id_bureau") %>%                  # summarize
  left_join(bureau,.,by = "sk_id_bureau") %>% 
  makedummies(basal_level = TRUE) %>% # make dummy
  select(-sk_id_bureau) %>%                       # not need
  SummarizeFunc(group = "sk_id_curr")             # summarize
credit_card_sum <- makedummies(credit_card,basal_level = TRUE) %>% # make dummy
  select(-sk_id_prev) %>% 
  SummarizeFunc(group = "sk_id_curr") 
install_pay_sum <- makedummies(install_pay,basal_level = TRUE) %>% # make dummy
  select(-sk_id_prev) %>% 
  SummarizeFunc(group = "sk_id_curr")
pos_cash_sum <- makedummies(pos_cash,basal_level = TRUE) %>% # make dummy
  select(-sk_id_prev) %>% 
  SummarizeFunc(group = "sk_id_curr")
previous_app_sum <- makedummies(previous_app,basal_level = TRUE) %>% # make dummy
  select(-sk_id_prev) %>% 
  SummarizeFunc(group = "sk_id_curr")

all_data_train <- app_train %>% 
  left_join(bureau_sum,by="sk_id_curr") %>% 
  left_join(credit_card_sum,by = "sk_id_curr") %>% 
  left_join(install_pay_sum,by = "sk_id_curr") %>% 
  left_join(pos_cash_sum,by = "sk_id_curr") %>% 
  left_join(previous_app_sum,by = "sk_id_curr")
all_data_test <- app_test %>% 
  left_join(bureau_sum,by="sk_id_curr") %>% 
  left_join(credit_card_sum,by = "sk_id_curr") %>% 
  left_join(install_pay_sum,by = "sk_id_curr") %>% 
  left_join(pos_cash_sum,by = "sk_id_curr") %>% 
  left_join(previous_app_sum,by = "sk_id_curr")
```

### Export

- not execute

```{r eval=FALSE}
write_csv(all_data_train,"~/Desktop/Home_Credit_Kaggle/input/csv_imp0/all_data_train.csv")
write_csv(all_data_test,"~/Desktop/Home_Credit_Kaggle/input/csv_imp0/all_data_test.csv")
```
