---
title: "Preprocess_ins_pay"
author: "kotsubo takuto"
output: 
    html_document:
      md_extensions: -ascii_identifiers
      toc: true
      toc_depth: 3
---

## Data description

- installments_payment.csv (8 variables)
    - Key variable: SK_ID_CURR, SK_ID_PREV
    - About: ローンの各月の支払い履歴

# Setting{.tabset .tabset-fade .tabset-pills}

## knitr option

```{r reset, include=FALSE}
# 初期化
rm(list = ls())
```

```{r set up, message=FALSE}
# set directory
setwd("~/Desktop/Home_Credit_Kaggle/") 
# max.print 
options(max.print="200", digits=5)
# Global options
library(knitr)
opts_chunk$set(echo=TRUE,
               cache = TRUE,
	             prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

## Library package

- 必要なパッケージを適宜追加

```{r package, message=FALSE}
library(tidyverse)
library(readr) # for csv
library(summarytools) # summary easily for EDA
library(GGally) # ggpairs
library(skimr) 
library(missForest)
library(imputeMissings)
library(mi)
library(doParallel)
library(qgraph)
library(psych)
library(fastcluster)
```

## Load funciton

```{r cache=FALSE}
source('~/Desktop/Home_Credit_Kaggle/script/function.R') # for preprocessing
source('~/Desktop/Home_Credit_Kaggle/script/makedummies.R') # for preprocessing
```

## read csv

- Missing value
na = c("XNA","NA","","NaN","?"): 以下の設定で naを計上する.

- convert charcter type into factor type

```{r}
# クレジット利用履歴 (by Credit Bureau)
install_pay <- read_csv("~/Desktop/Home_Credit_Kaggle/csv/installments_payments.csv",na = c("XNA","NA","","NaN","?")) %>% 
  mutate_if(is.character, funs(factor(.)))
```

# Preprocess

- Check for imputation values
- Describe the details on the explanation sheet
- Add `_imp` to the supplemented column
- Add `_add` to the added column

## impute missing values{.tabset .tabset-fade .tabset-pills}

- 検証内容
    - データ特性に従って欠損値を推定
    - 多重代入法などのアルゴリムに従って, 欠損値を推定

## add new column{.tabset .tabset-fade .tabset-pills}

- 新しい特徴量を作成する

```{r}
install_pay <- install_pay %>% 
  mutate(PAYMENT_PERC_add = AMT_PAYMENT / AMT_INSTALMENT,
         PAYMENT_DIFF_add = AMT_INSTALMENT - AMT_PAYMENT,
         DPD_add = DAYS_ENTRY_PAYMENT - DAYS_INSTALMENT,
         DBD_add = DAYS_INSTALMENT - DAYS_ENTRY_PAYMENT,
         DBD_DIFF_add = abs(DPD_add)) 
```

## Summarize

- *NAがInf or - Infになることに注意する*(max,min 計算時)

```{r}
install_pay <- makedummies(install_pay,basal_level = TRUE) %>% # make dummy
  select(-SK_ID_PREV) %>% 
  SummarizeFunc(group = "SK_ID_CURR") 
```

## output for csv

- Save the csv files in the csv_imp folder

```{r eval=TRUE}
write_csv(install_pay,"~/Desktop/Home_Credit_Kaggle/csv_imp/installments_payments_imp.csv")
```
