---
title: "Preprocess_bureau"
author: "kotsubo takuto"
output: 
    html_document:
      md_extensions: -ascii_identifiers
      toc: true
      toc_depth: 3
---

## Data description

- bureau.csv (17 variables)
    - Key variable: SK_ID_CURR, SK_ID_BUREAU 
    - About: 以前使用していた, 融資の履歴
- bureau_balance.csv (3 variables)
    - Key variable: SK_ID_BUREAU
    - About: `bureau.csv`の補助データ
    - MONTHS_BALANCE: 利用日に対応した, 月次のバランス?
    - STATUS: 月次のステータス, (active, closed, DPD0-30,… [C means closed, X means status unknown, 0 means no DPD, 1 means maximal did during month between 1-30, 2 means DPD 31-60,… 5 means DPD 120+ or sold or written off ] )

# Setting{.tabset .tabset-fade .tabset-pills}

## knitr option

```{r reset, include=FALSE}
# 初期化
rm(list = ls())
```

```{r set up, message=FALSE}
# set directory
setwd("~/Desktop/Home_Credit_Kaggle/") 
# max.print 
options(max.print="200", digits=5)
# Global options
library(knitr)
opts_chunk$set(echo=TRUE,
               cache = TRUE,
	             prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

## Library package

- 必要なパッケージを適宜追加

```{r package, message=FALSE}
library(tidyverse)
library(readr) # for csv
library(summarytools) # summary easily for EDA
library(GGally) # ggpairs
library(skimr) 
library(missForest)
library(imputeMissings)
library(mi)
library(doParallel)
library(qgraph)
library(psych)
library(fastcluster)
```

## Load funciton

```{r cache=FALSE}
source('~/Desktop/Home_Credit_Kaggle/script/function.R') # for preprocessing
```

## read csv

- Missing value
na = c("XNA","NA","","NaN","?"): 以下の設定で naを計上する.

- convert charcter type into factor type

```{r}
# クレジット利用履歴 (by Credit Bureau)
bureau <- read_csv("~/Desktop/Home_Credit_Kaggle/csv/bureau.csv",na = c("XNA","NA","","NaN","?")) %>% 
  mutate_if(is.character, funs(factor(.)))
bureau_balance <- read_csv("~/Desktop/Home_Credit_Kaggle/csv/bureau_balance.csv",na = c("XNA","NA","","NaN","?")) %>% 
  mutate_if(is.character, funs(factor(.)))
```

# Preprocess

- Check for imputation values
- Describe the details on the explanation sheet
- Add `_imp` to the supplemented column
- Add `_add` to the added column

## impute missing values{.tabset .tabset-fade .tabset-pills}

- 検証内容
    - データ特性に従って欠損値を推定
    - 多重代入法などのアルゴリムに従って, 欠損値を推定

## add new column{.tabset .tabset-fade .tabset-pills}

- 新しい特徴量を作成する

## output for csv

- Save the csv files in the csv_imp folder

```{r eval=TRUE}
write_csv(app_train,"~/Desktop/Home_Credit_Kaggle/csv_imp/bureau_imp.csv")
write_csv(app_test,"~/Desktop/Home_Credit_Kaggle/csv_imp/bureau_balance_imp.csv")
```
