---
title: "Preprocess_credit"
author: "kotsubo takuto"
output: 
    html_document:
      md_extensions: -ascii_identifiers
      toc: true
      toc_depth: 3
---

## Data description

- credit_card_balance.csv (23 variavbles)
    - Key variable: SK_ID_CURR, SK_ID_PREV
    - About: 各月毎のクレジットカード履歴,月次バランス

# Setting{.tabset .tabset-fade .tabset-pills}

## knitr option

```{r reset, include=FALSE}
# 初期化
rm(list = ls())
```

```{r set up, message=FALSE}
# set directory
setwd("~/Desktop/Home_Credit_Kaggle/") 
# max.print 
options(max.print="200", digits=5)
# Global options
library(knitr)
opts_chunk$set(echo=TRUE,
               cache = TRUE,
	             prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

## Library package

- 必要なパッケージを適宜追加

```{r package, message=FALSE}
library(tidyverse)
library(readr) # for csv
library(summarytools) # summary easily for EDA
library(GGally) # ggpairs
library(skimr) 
library(missForest)
library(imputeMissings)
library(mi)
library(doParallel)
library(qgraph)
library(psych)
library(fastcluster)
```

## Load funciton

```{r cache=FALSE}
source('~/Desktop/Home_Credit_Kaggle/script/function.R') # for preprocessing
source('~/Desktop/Home_Credit_Kaggle/script/makedummies.R') # for preprocessing
```

## read csv

- Missing value
na = c("XNA","NA","","NaN","?"): 以下の設定で naを計上する.

- convert charcter type into factor type

```{r}
# クレジット利用履歴 (by Credit Bureau)
credit_card <- read_csv("~/Desktop/Home_Credit_Kaggle/csv/credit_card_balance.csv",na = c("XNA","NA","","NaN","?")) %>% 
  mutate_if(is.character, funs(factor(.)))
```

# Preprocess

- Check for imputation values
- Describe the details on the explanation sheet
- Add `_imp` to the supplemented column
- Add `_add` to the added column

## Check value

```{r}
credit_card <- credit_card %>% 
  mutate(
    AMT_DRAWINGS_ATM_CURRENT = ifelse(AMT_DRAWINGS_ATM_CURRENT<0, 0, AMT_DRAWINGS_ATM_CURRENT),
    AMT_DRAWINGS_CURRENT = ifelse(AMT_DRAWINGS_CURRENT<0, 0, AMT_DRAWINGS_CURRENT)
  )
```

## impute missing values{.tabset .tabset-fade .tabset-pills}

- 検証内容
    - データ特性に従って欠損値を推定
    - 多重代入法などのアルゴリムに従って, 欠損値を推定

### CNT

- CNT_DRAWINGS_ATM_CURRENT
- CNT_DRAWINGS_CURRENT
- CNT_DRAWINGS_OTHER_CURRENT 
- CNT_DRAWINGS_POS_CURRENT 
- CNT_INSTALMENT_MATURE_CUM

```{r eval=FALSE}
credit_card %>% 
  select_if(grepl("CNT",names(.))) %>% 
  na.omit() %>%
  cor() %>% 
  qgraph(edge.labels=T)

credit_card %>% 
  select_if(grepl("CNT",names(.))) %>% 
  na.omit() %>%
  cor() %>% 
  cor.plot(numbers = TRUE)
```

```{r eval=FALSE}
# data
data1 <- credit_card %>% select_if(grepl("CNT",names(.)))
# str_c(a,collapse = "', '")
patterns <- c("CNT_DRAWINGS_ATM_CURRENT","CNT_DRAWINGS_OTHER_CURRENT", "CNT_DRAWINGS_POS_CURRENT","CNT_INSTALMENT_MATURE_CUM")
# 欠損値補完
tmp1 <- ImputeMissingValueRF(data1,patterns)

# データ結合
credit_card <- cbind(credit_card,tmp1)
```

## add new column{.tabset .tabset-fade .tabset-pills}

- 新しい特徴量を作成する

```{r eval=FALSE}
# need list
tmp <-  c("AMT_BALANCE","AMT_CREDIT_LIMIT_ACTUAL","AMT_DRAWINGS_CURRENT","AMT_PAYMENT_TOTAL_CURRENT","AMT_RECIVABLE")
# name list
patterns <- c( "CREDIT_CARD_TSNE_1", "CREDIT_CARD_TSNE_2")

tmp1 <- credit_card %>% 
  select_if(grepl(paste(tmp, collapse="|"),names(.))) %>% 
  ImputeMissingValueTSNE(patterns)

# データ結合
credit_card <- cbind(credit_card,tmp1)
```

### other

```{r}
credit_card <- credit_card %>% 
  mutate(
    CNT_ATM_INSTALMENT_PERC_add = CNT_DRAWINGS_ATM_CURRENT/CNT_INSTALMENT_MATURE_CUM,
    CNT_ALL_INSTALMENT_PERC_add = CNT_DRAWINGS_CURRENT/CNT_INSTALMENT_MATURE_CUM,
    CNT_OTHER_INSTALMENT_PERC_add = CNT_DRAWINGS_OTHER_CURRENT/CNT_INSTALMENT_MATURE_CUM,
    CNT_POS_INSTALMENT_PERC_add = CNT_DRAWINGS_POS_CURRENT/CNT_INSTALMENT_MATURE_CUM,
    AMT_BALANCE_LIMIT_PERC_add = AMT_BALANCE / AMT_CREDIT_LIMIT_ACTUAL,
    ATM_USING_DIFF_add = AMT_DRAWINGS_CURRENT - AMT_DRAWINGS_ATM_CURRENT
  )
```

## Summarize

- *NAがInf or - Infになることに注意する*(max,min 計算時)

```{r}
credit_card <- makedummies(credit_card,basal_level = TRUE) %>% # make dummy
  select(-SK_ID_PREV) %>% 
  SummarizeFunc(group = "SK_ID_CURR") 
```

## output for csv

- Save the csv files in the csv_imp folder

```{r eval=TRUE}
write_csv(credit_card,"~/Desktop/Home_Credit_Kaggle/csv_imp/credit_card_balance_imp.csv")
```
