---
title: "Home Credit Dafault Risk (EDA)"
author: "kotsubo takuto"
output: 
    html_document:
      md_extensions: -ascii_identifiers
      toc: true
      toc_depth: 3
      code_folding: hide
---

# Home Credit Default Risk

## Overview

- 多くの人々は, クレジット履歴の不足や欠如により, ローン契約に奮闘している.
そして不幸なことにこのような人々はしばしば, 信頼できない貸し手を利用している.

- そこでクレジット履歴に代替する, 電気通信会社や取引情報などを用いて, 対象者の返済能力を予測する.

## Data description

- application_{train|test}.csv (122|121 variables)
    - Key variable: SK_ID_CURR
    - Objective variable: TARGET(1:返済困難, 0: other, 連続値)
    - About: 全てのアプリケーションのデータ
- bureau.csv (17 variables)
    - Key variable: SK_ID_CURR, SK_ID_BUREAU 
    - About: 以前使用していた, 融資の履歴
- bureau_balance.csv (3 variables)
    - Key variable: SK_ID_BUREAU
    - About: `bureau.csv`の補助データ
    - MONTHS_BALANCE: 利用日に対応した, 月次のバランス?
    - STATUS: 月次のステータス, (active, closed, DPD0-30,… [C means closed, X means status unknown, 0 means no DPD, 1 means maximal did during month between 1-30, 2 means DPD 31-60,… 5 means DPD 120+ or sold or written off ] )
- previous_applications.csv (37 variables)
    - Key variable: SK_ID_CURR, SK_ID_PREV
    - About: サンプルで融資を受けているお客様のホームクレジットローンのすべての以前のアプリケーション
- installments_payment.csv (8 variables)
    - Key variable: SK_ID_CURR, SK_ID_PREV
    - About: 
- POS_CASH_balance.csv (8 variables)
    - Key variable: SK_ID_CURR, SK_ID_PREV
    - About: 
- credit_card_balance.csv (23 variavbles)
    - Key variable: SK_ID_CURR, SK_ID_PREV
    - About: 

## Toc

- Combine all table
- Overview data

# Setting{.tabset .tabset-fade .tabset-pills}

## knitr option

```{r reset, include=FALSE}
# 初期化
rm(list = ls())
```

```{r set up, message=FALSE}
# set directory
setwd("~/Desktop/Home_Credit_Kaggle/") 
# max.print 
options(max.print="200", digits=5)
# Global options
library(knitr)
opts_chunk$set(echo=TRUE,
               cache = FALSE,
	             prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

## Library package

- 必要なパッケージを適宜追加

```{r package, message=FALSE}
library(tidyverse)
library(readr) # for csv
library(summarytools) # summary easily for EDA
library(skimr) 
```

## read csv

- Missing value

na = c("XNA","NA","","NaN","?","Inf","-Inf"): 以下の設定で naを計上する.

- convert charcter type into factor type

```{r}
# 訓練データ, テストデータ
app_train <- read_csv("~/Desktop/Home_Credit_Kaggle/csv_imp/application_train_imp.csv",na = c("XNA","NA","","NaN","?","Inf","-Inf")) %>% 
    mutate_if(is.character, funs(factor(.)))
app_test <- read_csv("~/Desktop/Home_Credit_Kaggle/csv_imp/application_test_imp.csv",na = c("XNA","NA","","NaN","?","Inf","-Inf")) %>% 
  mutate_if(is.character, funs(factor(.)))
bureau <- read_csv("~/Desktop/Home_Credit_Kaggle/csv_imp/bureau_imp.csv",na = c("XNA","NA","","NaN","?","Inf","-Inf")) %>%
  mutate_if(is.character, funs(factor(.)))
credit_card <- read_csv("~/Desktop/Home_Credit_Kaggle/csv/credit_card_balance_imp.csv",na = c("XNA","NA","","NaN","?","Inf","-Inf")) %>% 
  mutate_if(is.character, funs(factor(.)))
install_pay <- read_csv("~/Desktop/Home_Credit_Kaggle/csv/installments_payments_imp.csv",na = c("XNA","NA","","NaN","?","Inf","-Inf")) %>% 
  mutate_if(is.character, funs(factor(.)))
pos_cash <- read_csv("~/Desktop/Home_Credit_Kaggle/csv/POS_CASH_balance_imp.csv",na = c("XNA","NA","","NaN","?","Inf","-Inf")) %>%
  mutate_if(is.character, funs(factor(.)))
previous_app <- read_csv("~/Desktop/Home_Credit_Kaggle/csv/previous_application_imp.csv",na = c("XNA","NA","","NaN","?","Inf","-Inf")) %>% 
  mutate_if(is.character, funs(factor(.)))
```

## combine table

```{r}
app_train <- app_train %>% 
  left_join(bureau,by="SK_ID_CURR") %>% 
  left_join(credit_card,by = "SK_ID_CURR") %>% 
  left_join(install_pay,by = "SK_ID_CURR") %>% 
  left_join(pos_cash,by = "SK_ID_CURR") %>% 
  left_join(previous_app,by = "SK_ID_CURR")

app_test <- app_test %>% 
  left_join(bureau,by="SK_ID_CURR") %>% 
  left_join(credit_card,by = "SK_ID_CURR") %>% 
  left_join(install_pay,by = "SK_ID_CURR") %>% 
  left_join(pos_cash,by = "SK_ID_CURR") %>% 
  left_join(previous_app,by = "SK_ID_CURR")
```

## overview

- check data

```{r}
skimr::skim_to_wide(app_train) %>% kable()
skimr::skim_to_wide(app_test) %>% kable()
dfSummarySplit(app_train)
dfSummarySplit(app_test)
```

## output for csv

- Save the csv files in the csv_imp folder

```{r eval=TRUE}
write_csv(app_train,"~/Desktop/Home_Credit_Kaggle/csv_imp/all_data_train.csv")
write_csv(app_test,"~/Desktop/Home_Credit_Kaggle/csv_imp/all_data_test.csv")
```
